Cannibalism among the supermassive black holes

### 2019-02-20 paper.tex
Worked mainly on Results section.

\subsection{AR-Chain code}
Summary of the code and the modifications we made.

@@

\subsection{Simulation setup}
For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
\begin{equation}\label{tfric}
    t_{fric} = \frac{19}{6}Gyr\left(\frac{R_e}{5kpc}\right)^2\frac{\sigma_{eff}}{200km\,s^{-1}}\frac{10^8\,M_{\odot}}{M_{bh}} \text{  s}.
\end{equation}
The orbiting black holes were injected into their host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Eqn. \ref{re}) following galaxy mergers.  Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{M(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.

\section{Results}\label{sec:results}

@@

@@

Finally, the black hole xray luminosity is estimated from:
\begin{equation}
    L_x = 0.01\dot{M}_{acc}c^2 \text{  erg s}^{-1}.
\end{equation}

>>>>

\subsection{Simulation Physics}
In this section, we describe the underlying physics of our simulations, including choice of galaxy background potential, BH diffusion through the galaxy, and gravitational wave kicks as a result of mergers.

@@

\subsection{Simulation setup}
For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
\begin{equation}\label{tfric}
    t_{fric} = \frac{19}{6}\left(\frac{R_e}{5kpc}\right)^2\frac{\sigma_{eff}}{200km\,s^{-1}}\frac{10^8\,M_{\odot}}{M_{bh}} \text{  Gyr}.
\end{equation}
The orbiting black holes were injected into their host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.  Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{GM(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.

\section{Results}\label{sec:results}
Here we review the primary results of our simulations, focusing on the various interactions of the orbiting black holes with their host SMBHs and the final luminosity characteristics of those that did not merge.

\subsection{Mergers, Ejections and Kicks}

Figure \ref{fig:fmeo}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Final Radius v Mass of Orbiting BHs_corrected_".png}
\caption{Final Radii of remaining orbital black holes at z=0}
\label{fig:mvr}
\end{center}
\end{figure}

@@

Finally, the black hole x-ray luminosity is estimated from:
\begin{equation}
    L_x = 0.01\dot{M}_{acc}c^2 \text{  erg s}^{-1}.
\end{equation}
